---
title: "SA_Ass1"
author: "Jakub Raszka"
date: "5 2 2021"
output: word_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# Packages
pacman::p_load(leaflet, htmltools, htmlwidgets, tidyverse, ggplot2, reader)

```

## Task
W1 - Make me an interactive map


1. Answer: Describe a problem or question in your field for which spatial analysis could be applicable.

Let's imagine a situation in which we can only hope to never occur, yet we know has happened, it is happening and it will happen again. In a given region, doctors have examined many patients across entire region whose symptoms resembled a severe intoxication. Yet, none of the patients has been in touch with any toxic substances. As the number of patients keeps rising, doctors in collaboration with advanced data specialists, a.k.a cognitive scientists, are determined to discover the source of suspected poisoning.
To do so, home and work address of all patients are obtained and mapped along with any locations wherein patients regularly spent substantial amount of their time.

2. Answer: List 5 data layers that you think are necessary to answer your question/solve your problem. Find on the internet github.and then describe examples of two or three of your listed layers.

There are many data layers required, to name a few, surface terrain (specifically hydrography), ownership and tax parcels, a layer of industrial network (factories, chemical plants, or any other establishment with potential of causing large-scale contamination), a layer of man-made infrastructure (roads, buildings),  and a list of potentially plausible substances produced in each factory. Lastly, a layer of all accidents in the region with fine temporal resolution. Likewise, the temporal resolution of patients movement and time of contagion is necessary.
The hydrography layer is important to map all water areas which could potentially connect a factory and patients through water. The significance of temporal layers lie in the possibility of discovering overlaps of accidents in patient's physical proximity in time. 
In such cases, if we imagine that usual tracking approaches fail, the number of is skyrocketing, there is always an option of using  personal data from patient's gadgets. Such a solution is highly controversial as we can see nowadays... 


3. Code: Your colleague has found some ruins during a hike in the Blue Mountains and recorded the coordinates of structures on her phone(RCFeature.csv). She would like to map her points but has no computer or mapping skills. Can you make a map that she can work with using only a browser? She needs an interactive map that she can download to her computer and use straightaway.

```{r}
# loading data
df <- read_csv("RCFeature.csv")

# filtering out 1 NA observation
df <- df %>% filter(!is.na(Longitude))


# trying out whether the setView is set at correct location, zoom with only 3 map layers
leaflet() %>%
  setView(lng = 150.2965, lat = -33.76165, zoom = 12) %>% 
  addProviderTiles("Esri.WorldPhysical") %>% 
 addProviderTiles("Esri.WorldImagery") %>% 
  addProviderTiles("MtbMap", group = "Geo") %>% 
  addAwesomeMarkers(lng = df$Longitude,
                    lat = df$Latitude, 
                    popup = df$FeatureType)


# Making an interactive map with multiple choice of map types, terrains

## setting initial view coordinate and zoom which we got from data  

l_den <- leaflet() %>%   # assign the base location to an object
  setView(150.2965, -33.76165, zoom = 12)


## creating a list with all possible map layers and  providers
esri <- grep("^Esri", providers, value = TRUE)

## putting them into a line so we don't have to repeat ourselves later on
for (provider in esri) {
  l_den <- l_den %>% addProviderTiles(provider, group = provider)
}


## setting features of the map
BM_map <- l_den %>%
  addLayersControl(baseGroups = names(esri),
                   options = layersControlOptions(collapsed = FALSE)) %>%
  
  # adding minimap and choosin gits layer, position in the map
  addMiniMap(tiles = esri[[1]], toggleDisplay = TRUE,
             position = "bottomright") %>%
  
  # adding a possibility of measuring distances
  addMeasure(
    position = "bottomleft",
    primaryLengthUnit = "meters",
    primaryAreaUnit = "sqmeters",
    activeColor = "#3D535D",
    completedColor = "#7D4479") %>% 
  htmlwidgets::onRender("
                        function(el, x) {
                        var myMap = this;
                        myMap.on('baselayerchange',
                        function (e) {
                        myMap.minimap.changeLayer(L.tileLayer.provider(e.name));
                        })
                        }") %>% 
  addControl("", position = "topright")


## the map is ready, now we shall align it with our desired locations 
BM_map <- BM_map %>% 
  addCircleMarkers(lng = df$Longitude, 
             lat = df$Latitude,
             
             #  clustering
             clusterOptions = markerClusterOptions(), # 
             
             # setting size by the accuracy (and multiplying for the ease of finding all of them)
             radius = df$Accuracy*1.5,
              
             
             # setting parameters of label when hoovered over a marker
             label = paste("FeatureId: ", df$FeatureID,
                           ",  Feature Type:", df$FeatureType,
                           ",  Description:", df$Description, sep = "\n"))

BM_map

# saving the map as html
#saveWidget(BM_map, "BM_map.html", selfcontained = TRUE)


# considered alternative for labels
# str_c(str_c("Feature ID:", df$FeatureID),
#                            str_c("Feature Type:", df$FeatureType, sep = " "),
#                            str_c("Description:", df$Description, sep = " "),
#                            sep = "<br/>")
```


4. Create a standalone .html map in Leaflet showing at least basic topography and relief, and load in the table of points. Make sure she can see the FeatureID, FeatureType and Description attributes when she hovers over the point markers. 

5. Consider adding elements such as minimap() and measure() for easier map interaction
6. Explore differentiating the markers (e.g. by size using Accuracy field)

7. Explore the option of clustering markers with addMarkers(clusterOptions = markerClusterOptions()). Do you recommend marker clustering here?

Given the density and immediate proximity of data locations, I think that clusteroptions is a nice improvement in viewing every single data point. However, if we just want to get a feeling for the distribution without any info about the data points, the cluster options, should be tagged out.



Submit here both a brief write up and the .R script and the .html map. Alternatively, submit answer to the questions and a link to Github repo where both files are deposited.











